A decentralized network support middleware for MMOGs

### 2009-09-10 trunk/textos/PlanoDoutorado/Lugano/short_planodoc_lugano.tex

\begin{table}[h]
\begin{center}
%\caption{Créditos a obter}
\label{tab:creditos}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|}
\hline
Task   & Sep & Oct & Nov & Dec & Jan & Fev & Mar & Apr & May \\ \hline \hline
Language course & X & X & X &   &   &   &   &   &  \\ \hline
1       & X &   &   &   &   &   &   &   &   \\ \hline
2 (a)   &   & X & X &   &   &   &   &   &   \\ \hline
2 (b)   &   &   &   & X & X &   &   &   &   \\ \hline
2 (c and d) & & &   &   &   & X & X &   &   \\ \hline
3           & & &   &   &   & X & X & X &   \\ \hline
4           & & &   &   &   &   &   &   & X \\ \hline
Writing of papers     & & & X & X & X & X & X & X & X \\ \hline

>>>>

\begin{table}[h]
\begin{center}
%\caption{Créditos a obter}
\label{tab:creditos}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|}
\hline
Task   & Sep & Oct & Nov & Dec & Jan & Feb & Mar & Apr & May \\ \hline \hline
Language course & X & X & X &   &   &   &   &   &  \\ \hline
1       & X &   &   &   &   &   &   &   &   \\ \hline
2 (a)   &   & X & X &   &   &   &   &   &   \\ \hline
2 (b)   &   &   &   & X & X &   &   &   &   \\ \hline
2 (c and d) & & &   &   &   & X & X &   &   \\ \hline
3           & & &   &   &   & X & X & X &   \\ \hline
4           & & &   &   &   &   &   &   & X \\ \hline
Writing of papers     & & & X & X & X & X & X & X & X \\ \hline
